%-------------------------
% Resume in LaTeX
% Author: Gujjari Sai Sanjana
% Based on the widely used "Jake's Resume" template
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}

%----------PAGE LAYOUT----------
\pagestyle{fancy}
\fancyhf{}                 % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
%-------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt, parsep=1pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sai Sanjana Gujjari} \\ \vspace{3pt}
    {\small \textbf{Full-Stack Developer}} \\ \vspace{4pt}
    \small
    Hyderabad, India $|$ +91 78425 02935 $|$
    \href{mailto:gujjarisaisanjana@gmail.com}{\underline{gujjarisaisanjana@gmail.com}} \\ \vspace{2pt}
    \href{https://saisanjana.vercel.app/}{\underline{Portfolio}} $|$
    \href{https://www.linkedin.com/in/sai-sanjana-gujjari}{\underline{LinkedIn}} $|$
    \href{https://github.com/GujjariSaiSanjana}{\underline{GitHub}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Full-Stack Developer skilled in \textbf{React, Next.js, Node.js, and Python}, with internship experience shipping production features at fast-paced startups. Built \textbf{AI-powered tools (RAG and LLM agents)}, delivered a certificate-verification system that cut manual effort by \textbf{30\%}, and optimized a frontend that improved mobile performance by \textbf{25\%}. Strong in \textbf{REST API design, database integration, AWS deployment, clean architecture, and Agile delivery}.}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Frontend Developer Intern}{May 2025 -- Jul 2025}
    {Secnode}{Remote}
    \resumeItemListStart
      \resumeItem{Optimized a \textbf{large-scale Next.js application} with lazy loading, code splitting, and efficient data fetching.}
      \resumeItem{Integrated content workflows with \textbf{Sanity CMS} for dynamic content rendering and easier maintenance.}
      \resumeItem{Aligned \textbf{TypeScript backend APIs} with frontend data contracts to reduce integration issues.}
      \resumeItem{Reduced API response latency by streamlining request handling and frontend-to-backend communication.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Engineer Intern}{Jan 2025 -- Apr 2025}
    {Knowvation Learning Pvt. Ltd}{Remote}
    \resumeItemListStart
      \resumeItem{Built a scalable \textbf{certificate verification system} with unique-ID validation, cutting manual verification effort by \textbf{30\%}.}
      \resumeItem{Developed a responsive frontend in \textbf{TypeScript, React, and Tailwind CSS}, improving mobile performance by \textbf{25\%}.}
      \resumeItem{Designed and tested \textbf{REST API} workflows in Postman, optimizing query performance and release speed.}
      \resumeItem{Managed version control and automated deployments using \textbf{Git and CI/CD pipelines}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{\href{https://github.com/GujjariSaiSanjana/Ai-traveller-agent}{\underline{AI Traveller Agent}}} $|$ \emph{TypeScript, AI Agent, LLM}}{}
    \resumeItemListStart
      \resumeItem{Built an AI agent that turns a single prompt into a structured, day-by-day trip itinerary, orchestrating LLM calls with tool use.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://github.com/GujjariSaiSanjana/SAST-Agent}{\underline{SAST Agent}}} $|$ \emph{TypeScript, Security, AI}}{}
    \resumeItemListStart
      \resumeItem{Developed a \textbf{static application security testing} agent that scans source code and surfaces vulnerabilities, pairing rule-based analysis with LLM-assisted reasoning.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://github.com/GujjariSaiSanjana/Pdf-RAG}{\underline{RAG Applications (PDF, Web, Education)}}} $|$ \emph{Python, TypeScript, RAG}}{}
    \resumeItemListStart
      \resumeItem{Built \textbf{Retrieval-Augmented Generation} apps over PDFs, web pages, and course material using chunking, embeddings, and vector retrieval to keep answers grounded.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://github.com/GujjariSaiSanjana/Waste_recycling}{\underline{Waste Recycling Management System}}} $|$ \emph{TypeScript, React.js, REST}}{}
    \resumeItemListStart
      \resumeItem{Built a full-stack waste-tracking app with a responsive React frontend and REST APIs in 24 hours; won \textbf{3rd prize} among 80+ teams.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \item[]
    \small{
      \textbf{Languages:} JavaScript, TypeScript, Python, Java, SQL \\ \vspace{2pt}
      \textbf{Frontend:} React.js, Next.js, Tailwind CSS, Bootstrap \\ \vspace{2pt}
      \textbf{Backend:} Node.js, Express.js, REST APIs, Microservices \\ \vspace{2pt}
      \textbf{AI / ML:} RAG, LLM APIs, Embeddings, Vector Search, AI Agents \\ \vspace{2pt}
      \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis \\ \vspace{2pt}
      \textbf{Cloud \& Tools:} AWS (EC2, S3, Lambda), Git, GitHub Actions, Postman, Linux
    }
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Science in Computer Science}{2022 -- 2026}
    {Vishwa Vishwani Institute of Systems and Management}{Hyderabad, India}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
  \item[]
    \small{
      \textbf{NxtWave (CCBP):} Developer Foundations, JavaScript Essentials, Dynamic Web Applications, Responsive Web Design (Flexbox), Node.js, Introduction to Databases.
    }
\resumeSubHeadingListEnd
\vspace{-4pt}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{\textbf{Co-Founder \& Mentor, CodeXP Club:} Mentored students in full-stack development and led technical sessions.}
    \resumeItem{\textbf{Hackathon, 3rd Prize:} Built a full-stack waste management system in 24 hours among 80+ teams.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
